Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-02-15 ms.tex
relabel figs

@@

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux ratio is $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.  We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit. The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 10$ K on the dayside. The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The inversion is not present on the nightside. The transmission spectrum is featureless, but consistent with the small features expected from cloud-free models. Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.  We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
\end{abstract}

@@

The photometric analyses are summarized for each observing season in Table\,\ref{tab:photometry}.  The standard deviation of WASP-103's brightness in each season is given in column~4.  The mean of the three standard deviations is 0.0058~mag, which is very comparable to the mean standard deviation of the six comparison stars (0.0055~mag).  To maximize the possibility of detecting WASP-103's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing any long-term variability in WASP-103 and/or the comparison stars (Figure\,\ref{fig:photometry}, top panel).  To estimate the stellar rotation period, we performed a periodogram analysis of the normalized data set based on least-squares fitting of sine curves.  The resulting frequency spectrum and the phase curve computed with the best period are shown in the middle and lower panels of Figure\,\ref{fig:photometry} respectively. The best-fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days \citep[based on the projected stellar rotation velocity reported in][]{gillon14}. The peak-to-peak variability amplitude is 0.005 mag.  Based on the formalism in \cite{zellem17}, we calculate that this variability will bias the measured eclipse depth by $\lesssim10$\,parts per million (ppm) from epoch to epoch, which is well below the photon-limited precision of our measurements.

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/photometry.eps}
\caption{$Top$: The normalized nightly Cousins $R$ band photometric dataset for WASP-103, acquired with the C14 automated imaging telescope at Fairborn Observatory. Vertical dashed lines denote separate observing seasons. Gaps are due to target visibility and the Arizona monsoon season (July - September). $Middle$: The frequency spectrum of the normalized dataset suggests low-amplitude variability with a period of 6.814~days. $Bottom$: The normalized dataset phased to the 6.814-day period, which we interpret as rotational modulation of a star spot or spots. A least-squares sine fit to the 6.814-day rotation period gives a peak-to-peak amplitude of just 0.005~mag.}
\label{fig:photometry}
\end{figure}

\begin{deluxetable}{ccccc}
	\tablewidth{0pt}
	\tablecaption{Photometric Observations of WASP-103 \label{tab:photometry}}
	\tablehead{
		\colhead{Observing} & \colhead{} & \colhead{Date Range} &
	\colhead{Sigma} & \colhead{Seasonal Mean} \\
		& \colhead{\,} & \colhead{\,} & \colhead{(mag)} & \colhead{(mag)}}
	\startdata
	   2014   &  59 & 56722--56972 & 0.0057 & $0.9546\pm0.0007$  \\
	   2015   &  73 & 57028--57335 & 0.0062 & $0.9549\pm0.0007$  \\
	   2016   &  26 & 57385--57451 & 0.0055 & $0.9485\pm0.0011$  \\
	\enddata
\end{deluxetable}

\section{Light Curve Fits}
\label{sec:fits}
We fit a two-component model to the light curves. One component models the astrophysical signal (the planet's thermal phase variation and transit), and the other component models the systematic noise introduced by time-dependent changes in instrument performance. For each light curve, we fit the physical and systematic components simultaneously, such that the total observed flux as a function of time is given by $F(t) = F_\mathrm{physical}(t) \times F_\mathrm{sys}(t)$. For the \HST\ data, where we observed two phase curves and two additional eclipses, we constrain the physical parameters to be the same for all visits, but allow some of the systematics parameters to vary (for more details see \S\,\ref{sec:hst_sys}). We fit the WFC3 band-integrated ``white" light curve, as well as spectroscopic light curves created from 10 wavelength bins uniformly spaced at $0.05\,\mu$m intervals between $1.15$ and $1.65\,\mu$m.

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/ellipsoidal.pdf}
\caption{Projected area of the planet as a function of orbital phase, normalized to unity at phase zero. The area variation was predicted analytically using the model from \cite{leconte11b}.}
\label{fig:ellipsoidal}
\end{figure}

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/systematics.pdf}
\caption{Raw light curves for WASP-103b observed with \HST/WFC3 (top panel) and \Spitzer/IRAC (bottom two panels). The data points are indicated with black dots. The \HST\ data are unbinned, and the Spitzer data are binned in time segments of 15 minutes with error bars indicating the bin standard deviation. The colored lines show the best fit models, which include the astrophysical signal and instrument systematics. The gray lines indicate the contribution from the instrument systematics alone (which would be observed for a source with constant brightness and no planet). For visual clarity, we corrected the \HST\ data for the upstream-downstream effect, separated the four visits by adding a flux offset, and zoomed in on the phase variation, so the transits are not displayed in the panel.}
\label{fig:systematics}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/rms.pdf}
\caption{Root mean square (rms) variability in the light curves as a function of bin size (black lines) compared to the expected rms from photon noise (colored lines). The central wavelength of the light curve is indicated in the upper right corner of each panel. With the exception of the \Spitzer\ 3.6 $\mu$m channel, the rms for the light curves bins down in agreement with predictions from the photon noise.}
\label{fig:rms}
\end{figure}

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/phase_curves_spherical.pdf}
\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom). For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1. The left column shows the phase curves with systematic noise removed (black points) compared to the best fit spherical harmonics model (colored lines). The error bars denote $1\,\sigma$ uncertainties (in some cases, the errors are smaller than the data points).  We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve.}
\label{fig:phasecurves}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
\caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag4}$. Phases $\phi=0.5$ and $0.0$ correspond to times of secondary eclipse and transit, when the substellar and antistellar points are respectively aimed at Earth. The blackbody model is fit to the \HST/WFC3 data only.}
\label{fig:spectra}
\end{figure*}

\begin{figure*}
\includegraphics[width = 1.0\textwidth, trim={1.5cm 0 0.5cm 0},clip]{Figures/hst_model_comparison.pdf}
\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag4}$ GCM. We also show the measured planet-to-star flux for each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} Temperature maps from the best fit models and the GCM at a pressure of 0.1 bar.}
\label{fig:model_comparison}
\end{figure*}

\begin{deluxetable*}{lllllllllll}
	\tablecolumns{11}
	\tablewidth{0pt}
	\tablecaption{Phase-Resolved Emission Spectra\tablenotemark{1} \label{table:spectra}}
	\tablehead{
	\colhead{$\lambda$} & \colhead{Dilution} & \colhead{$\phi = 0.1$} & \colhead{$\phi = 0.2$} & \colhead{$\phi = 0.3$} & \colhead{$\phi = 0.4$} & \colhead{$\phi = 0.5$} & \colhead{$\phi = 0.6$} & \colhead{$\phi = 0.7$} & \colhead{$\phi = 0.8$} & \colhead{$\phi = 0.9$}}
		\startdata
		1.175 & 0.10 & $ 179 \pm 79 $ & $ 411 \pm 77 $ & $ 647 \pm 80 $ & $ 1143 \pm 65 $ & $ 1259 \pm 47 $ & $ 1063 \pm 64 $ & $ 710 \pm 73 $ & $ 412 \pm 78 $ & $ 177 \pm 79 $ \\ 
		1.225 & 0.11 & $ 188 \pm 76 $ & $ 398 \pm 74 $ & $ 928 \pm 77 $ & $ 1276 \pm 62 $ & $ 1448 \pm 46 $ & $ 1216 \pm 62 $ & $ 888 \pm 71 $ & $ 539 \pm 75 $ & $ 280 \pm 76 $ \\ 
		1.275 & 0.11 & $ 166 \pm 76 $ & $ 379 \pm 74 $ & $ 869 \pm 77 $ & $ 1323 \pm 62 $ & $ 1480 \pm 46 $ & $ 1282 \pm 62 $ & $ 814 \pm 71 $ & $ 515 \pm 75 $ & $ 247 \pm 76 $ \\ 
		1.325 & 0.11 & $ 266 \pm 75 $ & $ 432 \pm 73 $ & $ 904 \pm 76 $ & $ 1357 \pm 62 $ & $ 1498 \pm 45 $ & $ 1267 \pm 61 $ & $ 925 \pm 70 $ & $ 552 \pm 74 $ & $ 333 \pm 75 $ \\ 
		1.375 & 0.12 & $ 189 \pm 81 $ & $ 514 \pm 78 $ & $ 928 \pm 82 $ & $ 1376 \pm 66 $ & $ 1611 \pm 48 $ & $ 1411 \pm 65 $ & $ 954 \pm 75 $ & $ 461 \pm 79 $ & $ 292 \pm 81 $ \\ 
		1.425 & 0.13 & $ 238 \pm 79 $ & $ 532 \pm 76 $ & $ 1198 \pm 79 $ & $ 1431 \pm 64 $ & $ 1718 \pm 47 $ & $ 1511 \pm 64 $ & $ 1063 \pm 73 $ & $ 605 \pm 77 $ & $ 338 \pm 79 $ \\ 
		1.475 & 0.14 & $ 191 \pm 81 $ & $ 527 \pm 79 $ & $ 1068 \pm 82 $ & $ 1460 \pm 66 $ & $ 1667 \pm 48 $ & $ 1392 \pm 66 $ & $ 1090 \pm 75 $ & $ 580 \pm 80 $ & $ 268 \pm 81 $ \\ 
		1.525 & 0.14 & $ 143 \pm 84 $ & $ 478 \pm 81 $ & $ 1048 \pm 85 $ & $ 1429 \pm 69 $ & $ 1623 \pm 50 $ & $ 1367 \pm 68 $ & $ 943 \pm 77 $ & $ 607 \pm 82 $ & $ 291 \pm 84 $ \\ 
		1.575 & 0.15 & $ 367 \pm 88 $ & $ 761 \pm 85 $ & $ 1088 \pm 89 $ & $ 1581 \pm 72 $ & $ 1749 \pm 52 $ & $ 1503 \pm 71 $ & $ 1107 \pm 81 $ & $ 754 \pm 86 $ & $ 422 \pm 88 $ \\ 
		1.625 & 0.16 & $ 359 \pm 93 $ & $ 565 \pm 90 $ & $ 1169 \pm 94 $ & $ 1590 \pm 76 $ & $ 1843 \pm 56 $ & $ 1593 \pm 75 $ & $ 1142 \pm 86 $ & $ 542 \pm 91 $ & $ 351 \pm 93 $ \\ 
		3.6 & 0.17 & $ 1148 \pm 333 $ & $ 3633 \pm 330 $ & $ 4487 \pm 320 $ & $ 4107 \pm 314 $ & $ 4458 \pm 383 $ & $ 3495 \pm 315 $ & $ 3720 \pm 330 $ & $ 2102 \pm 331 $ & $ 1431 \pm 334 $ \\ 
		4.5 & 0.16 & $ 1586 \pm 220 $ & $ 3468 \pm 214 $ & $ 4188 \pm 190 $ & $ 5334 \pm 179 $ & $ 5686 \pm 138 $ & $ 4904 \pm 183 $ & $ 3626 \pm 214 $ & $ 2575 \pm 217 $ & $ 1057 \pm 221 $ \\ 
		\enddata
		\tablenotetext{1}{The planet-to-star flux in each phase bin $\phi$ is in units of ppm.}
		%\vspace{-0.8cm}
	\end{deluxetable*}

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/twopanel_dayside_spectrum.pdf}
\caption{Dayside planet-to-star flux (points) compared to a blackbody model for the planet (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right). The 1D model was fit to all the data simultaneously, but the blackbody was fit to the WFC3 data only. The best fit 1D model binned at the resolution of the \Spitzer\ data is indicated by blue squares (right).} 
\label{fig:dayside}
\end{figure*}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/w103b_transmission_spectrum.pdf}
\caption{The transmission spectrum of WASP-103b, corrected for planet nightside emission at 1700 K (blue points) and uncorrected (red points). The dark gray line is the model transmission spectrum from the $\tau_\mathrm{drag4}$ GCM. Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.9$ m/s$^2$, and a temperature $T = 2410$ K).}
\label{fig:tspec}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/xsec_FULL.pdf}
\caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure and temperature (5 mbar, 3036 K). The strong CO feature at 4.5\,$\mu$m contributes to the high planet-to-star flux at that wavelength.  Water, hydrides/oxides, and the H- bound-free opacities all play a role in shaping the \HST/WFC3 spectrum.}
\label{fig:opacities}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/atmosphere_summary.pdf}
\caption{Summary of the 1D self-consistent model atmosphere fits to the dayside emission spectrum.  The temperature-pressure profile (top axis) is indicated by the 1-sigma spread of 500 randomly drawn T-P profiles from the posterior (light red) and a representative fit, with $f$=0.4, [M/H]=1.5, and C/O=0.7 (dark red).  The normalized thermal emission contribution functions for the \Spitzer\ points are shown in solid red, the WFC3 in-water band ($1.33-1.48\,\mu$m) in dark blue, and WFC3 out-of-water-band in light blue.  The observations probe between $\sim0.01$ and 0.001 bar, just above the tropopause region of the atmosphere where the temperature is increasing.  The dashed curves are thermochemical equilibrium mixing ratios for important absorbers computed along the representative fit's self-consistent T-P profile.  Note the rapid dissociation of water above the $\sim10$ mbar level where the inversion begins.}
\label{fig:summary}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs.pdf}
\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum. The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% credible interval. The blue lines correspond to solar metallicity (1) and C/O (0.54). The 2D histograms mark the 1, 2, and 3$\,\sigma$ credible regions in dark, medium, and light blue, respectively.}
\label{fig:composition}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/gcm_comparison.pdf}
\caption{GCM predictions (colored lines) compared to the best fit spherical harmonics model for the WFC3 white light, \Spitzer\ 3.6, and \Spitzer\ 4.5 micron phase curves (black lines, top to bottom). The nominal model is solar composition, cloud-free, with TiO/VO opacity and no drag. The models are corrected for the predicted ellipsoidal variability of the planet.}
\label{fig:gcmcomparison}
\end{figure}

>>>>

\author{Michael H. Williamson}
\affiliation{Center of Excellence in Information Systems, Tennessee State University, Nashville, TN 37209, USA}

@@

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux ratio is $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.  We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit. The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside. The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The inversion is not present on the nightside. The transmission spectrum is featureless, but consistent with the small features expected from cloud-free models. Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.  We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
\end{abstract}

@@

The photometric analyses are summarized for each observing season in Table\,\ref{tab:photometry}.  The standard deviation of WASP-103's brightness in each season is given in column~4.  The mean of the three standard deviations is 0.0058~mag, which is comparable to the mean standard deviation of the six comparison stars (0.0055~mag).  To maximize the possibility of detecting WASP-103's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing any long-term variability in WASP-103 and/or the comparison stars (Figure\,\ref{fig:photometry}, top panel).  To estimate the stellar rotation period, we performed a periodogram analysis of the normalized data set based on least-squares fitting of sine curves.  The resulting frequency spectrum and the phase curve computed with the best period are shown in the middle and lower panels of Figure\,\ref{fig:photometry} respectively. The best-fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days \citep[based on the projected stellar rotation velocity reported in][]{gillon14}. The peak-to-peak variability amplitude is 0.005 mag.  Based on the formalism in \cite{zellem17}, we calculate that this variability will bias the measured eclipse depth by $\lesssim10$\,parts per million (ppm) from epoch to epoch, which is well below the photon-limited precision of our measurements.

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/photometry.eps}
\caption{$Top$: The normalized nightly Cousins $R$ band photometric dataset for WASP-103, acquired with the C14 automated imaging telescope at Fairborn Observatory. Vertical dashed lines denote separate observing seasons. Gaps are due to target visibility and the Arizona monsoon season (July - September). $Middle$: The frequency spectrum of the normalized dataset suggests low-amplitude variability with a period of 6.814~days. $Bottom$: The normalized dataset phased to the 6.814-day period, which we interpret as rotational modulation of a star spot or spots. A least-squares sine fit to the 6.814-day rotation period gives a peak-to-peak amplitude of just 0.005~mag.}
\label{fig:photometry}
\end{figure}
\begin{deluxetable}{ccccc}
	\tablewidth{0pt}
	\tablecaption{Photometric Observations of WASP-103 \label{tab:photometry}}
	\tablehead{
	\colhead{Observing} & \colhead{} & \colhead{Date Range} &
	\colhead{Sigma} & \colhead{Seasonal Mean} \\
		& \colhead{\,} & \colhead{\,} & \colhead{(mag)} & \colhead{(mag)}}
	\startdata
	   2014   &  59 & 56722--56972 & 0.0057 & $0.9546\pm0.0007$  \\
	   2015   &  73 & 57028--57335 & 0.0062 & $0.9549\pm0.0007$  \\
	   2016   &  26 & 57385--57451 & 0.0055 & $0.9485\pm0.0011$  \\
	\enddata
\end{deluxetable}

\section{\HST\ and \Spitzer\ Light Curve Fits}
\label{sec:fits}
We fit a two-component model to the light curves. One component models the astrophysical signal (the planet's thermal phase variation and transit), and the other component models the systematic noise introduced by time-dependent changes in instrument performance. For each light curve, we fit the physical and systematic components simultaneously, such that the total observed flux as a function of time is given by $F(t) = F_\mathrm{physical}(t) \times F_\mathrm{sys}(t)$. For the \HST\ data, where we observed two phase curves and two additional eclipses, we constrain the physical parameters to be the same for all visits, but allow some of the systematics parameters to vary (for more details see \S\,\ref{sec:hst_sys}). We fit the WFC3 band-integrated ``white" light curve, as well as spectroscopic light curves created from 10 wavelength bins uniformly spaced at $0.05\,\mu$m intervals between $1.15$ and $1.65\,\mu$m.

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/fig2.pdf}
\caption{Projected area of the planet as a function of orbital phase, normalized to unity at phase zero. The area variation was predicted analytically using the model from \cite{leconte11b}.}
\label{fig:ellipsoidal}
\end{figure}

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/fig3.pdf}
\caption{Raw light curves for WASP-103b observed with \HST/WFC3 (top panel) and \Spitzer/IRAC (bottom two panels). The data points are indicated with black dots. The \HST\ data are unbinned, and the Spitzer data are binned in time segments of 15 minutes with error bars indicating the bin standard deviation. The colored lines show the best fit models, which include the astrophysical signal and instrument systematics. The gray lines indicate the contribution from the instrument systematics alone (which would be observed for a source with constant brightness and no planet). For visual clarity, we corrected the \HST\ data for the upstream-downstream effect, separated the four visits by adding a flux offset, and zoomed in on the phase variation, so the transits are not displayed in the panel.}
\label{fig:systematics}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/fig4.pdf}
\caption{Root mean square (rms) variability in the light curves as a function of bin size (black lines) compared to the expected rms from photon noise (colored lines). The central wavelength of the light curve is indicated in the upper right corner of each panel. With the exception of the \Spitzer\ 3.6 $\mu$m channel, the rms for the light curves bins down in agreement with predictions from the photon noise.}
\label{fig:rms}
\end{figure}

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/fig5.pdf}
\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom). For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1. The left column shows the phase curves with systematic noise removed (black points) compared to the best fit spherical harmonics model (colored lines). The error bars denote $1\,\sigma$ uncertainties (in some cases, the errors are smaller than the data points).  We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve.}
\label{fig:phasecurves}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/fig6.pdf}
\caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag4}$. Phases $\phi=0.5$ and $0.0$ correspond to times of secondary eclipse and transit, when the substellar and antistellar points are respectively aimed at Earth. The blackbody model is fit to the \HST/WFC3 data only.}
\label{fig:spectra}
\end{figure*}

\begin{figure*}
\includegraphics[width = 1.0\textwidth, trim={1.5cm 0 0.5cm 0},clip]{Figures/fig7.pdf}
\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM. The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag4}$ GCM. We also show the measured planet-to-star flux for each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.  \textbf{Right:} Temperature maps from the best fit models and the GCM at a pressure of 0.1 bar.}
\label{fig:model_comparison}
\end{figure*}

\begin{deluxetable*}{lllllllllll}
	\tablecolumns{11}
	\tablewidth{0pt}
	\tablecaption{Phase-Resolved Emission Spectra\tablenotemark{1} \label{table:spectra}}
	\tablehead{
	\colhead{$\lambda$} & \colhead{Dilution} & \colhead{$\phi = 0.1$} & \colhead{$\phi = 0.2$} & \colhead{$\phi = 0.3$} & \colhead{$\phi = 0.4$} & \colhead{$\phi = 0.5$} & \colhead{$\phi = 0.6$} & \colhead{$\phi = 0.7$} & \colhead{$\phi = 0.8$} & \colhead{$\phi = 0.9$}}
		\startdata
		1.175 & 0.10 & $ 179 \pm 79 $ & $ 411 \pm 77 $ & $ 647 \pm 80 $ & $ 1143 \pm 65 $ & $ 1259 \pm 47 $ & $ 1063 \pm 64 $ & $ 710 \pm 73 $ & $ 412 \pm 78 $ & $ 177 \pm 79 $ \\ 
		1.225 & 0.11 & $ 188 \pm 76 $ & $ 398 \pm 74 $ & $ 928 \pm 77 $ & $ 1276 \pm 62 $ & $ 1448 \pm 46 $ & $ 1216 \pm 62 $ & $ 888 \pm 71 $ & $ 539 \pm 75 $ & $ 280 \pm 76 $ \\ 
		1.275 & 0.11 & $ 166 \pm 76 $ & $ 379 \pm 74 $ & $ 869 \pm 77 $ & $ 1323 \pm 62 $ & $ 1480 \pm 46 $ & $ 1282 \pm 62 $ & $ 814 \pm 71 $ & $ 515 \pm 75 $ & $ 247 \pm 76 $ \\ 
		1.325 & 0.11 & $ 266 \pm 75 $ & $ 432 \pm 73 $ & $ 904 \pm 76 $ & $ 1357 \pm 62 $ & $ 1498 \pm 45 $ & $ 1267 \pm 61 $ & $ 925 \pm 70 $ & $ 552 \pm 74 $ & $ 333 \pm 75 $ \\ 
		1.375 & 0.12 & $ 189 \pm 81 $ & $ 514 \pm 78 $ & $ 928 \pm 82 $ & $ 1376 \pm 66 $ & $ 1611 \pm 48 $ & $ 1411 \pm 65 $ & $ 954 \pm 75 $ & $ 461 \pm 79 $ & $ 292 \pm 81 $ \\ 
		1.425 & 0.13 & $ 238 \pm 79 $ & $ 532 \pm 76 $ & $ 1198 \pm 79 $ & $ 1431 \pm 64 $ & $ 1718 \pm 47 $ & $ 1511 \pm 64 $ & $ 1063 \pm 73 $ & $ 605 \pm 77 $ & $ 338 \pm 79 $ \\ 
		1.475 & 0.14 & $ 191 \pm 81 $ & $ 527 \pm 79 $ & $ 1068 \pm 82 $ & $ 1460 \pm 66 $ & $ 1667 \pm 48 $ & $ 1392 \pm 66 $ & $ 1090 \pm 75 $ & $ 580 \pm 80 $ & $ 268 \pm 81 $ \\ 
		1.525 & 0.14 & $ 143 \pm 84 $ & $ 478 \pm 81 $ & $ 1048 \pm 85 $ & $ 1429 \pm 69 $ & $ 1623 \pm 50 $ & $ 1367 \pm 68 $ & $ 943 \pm 77 $ & $ 607 \pm 82 $ & $ 291 \pm 84 $ \\ 
		1.575 & 0.15 & $ 367 \pm 88 $ & $ 761 \pm 85 $ & $ 1088 \pm 89 $ & $ 1581 \pm 72 $ & $ 1749 \pm 52 $ & $ 1503 \pm 71 $ & $ 1107 \pm 81 $ & $ 754 \pm 86 $ & $ 422 \pm 88 $ \\ 
		1.625 & 0.16 & $ 359 \pm 93 $ & $ 565 \pm 90 $ & $ 1169 \pm 94 $ & $ 1590 \pm 76 $ & $ 1843 \pm 56 $ & $ 1593 \pm 75 $ & $ 1142 \pm 86 $ & $ 542 \pm 91 $ & $ 351 \pm 93 $ \\ 
		3.6 & 0.17 & $ 982 \pm 271 $ & $ 3474 \pm 268 $ & $ 4309 \pm 255 $ & $ 4060 \pm 248 $ & $ 4458 \pm 383 $ & $ 3524 \pm 249 $ & $ 3725 \pm 267 $ & $ 1865 \pm 269 $ & $ 1116 \pm 272 $ \\ 
		4.5 & 0.16 & $ 1560 \pm 220 $ & $ 3347 \pm 213 $ & $ 4150 \pm 189 $ & $ 5240 \pm 178 $ & $ 5686 \pm 138 $ & $ 4995 \pm 181 $ & $ 3677 \pm 212 $ & $ 2403 \pm 213 $ & $ 921 \pm 219 $ \\ 
		\enddata
		\tablenotetext{1}{The planet-to-star flux in each phase bin $\phi$ is in units of ppm.}
	\end{deluxetable*}

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/fig8.pdf}
\caption{Dayside planet-to-star flux (points) compared to a blackbody model for the planet (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right). The 1D model was fit to all the data simultaneously, but the blackbody was fit to the WFC3 data only. The best fit 1D model binned at the resolution of the \Spitzer\ data is indicated by blue squares (right).} 
\label{fig:dayside}
\end{figure*}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/fig9.pdf}
\caption{The transmission spectrum of WASP-103b, corrected for planet nightside emission at 1700 K (blue points) and uncorrected (red points). The dark gray line is the model transmission spectrum from the $\tau_\mathrm{drag4}$ GCM. Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.9$ m/s$^2$, and a temperature $T = 2410$ K).}
\label{fig:tspec}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/fig10.pdf}
\caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure and temperature (5 mbar, 3036 K). The strong CO feature at 4.5\,$\mu$m contributes to the high planet-to-star flux at that wavelength.  Water, hydrides/oxides, and the H- bound-free opacities all play a role in shaping the \HST/WFC3 spectrum.}
\label{fig:opacities}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/fig11.pdf}
\caption{Summary of the 1D self-consistent model atmosphere fits to the dayside emission spectrum.  The temperature-pressure profile (top axis) is indicated by the 1-sigma spread of 500 randomly drawn T-P profiles from the posterior (light red) and a representative fit, with $f$=0.4, [M/H]=1.5, and C/O=0.7 (dark red).  The normalized thermal emission contribution functions for the \Spitzer\ points are shown in solid red, the WFC3 in-water band ($1.33-1.48\,\mu$m) in dark blue, and WFC3 out-of-water-band in light blue.  The observations probe between $\sim0.01$ and 0.001 bar, just above the tropopause region of the atmosphere where the temperature is increasing.  The dashed curves are thermochemical equilibrium mixing ratios for important absorbers computed along the representative fit's self-consistent T-P profile.  Note the rapid dissociation of water above the $\sim10$ mbar level where the inversion begins.}
\label{fig:summary}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/fig12.pdf}
\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum. The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% credible interval. The blue lines correspond to solar metallicity (1) and C/O (0.54). The 2D histograms mark the 1, 2, and 3$\,\sigma$ credible regions in dark, medium, and light blue, respectively.}
\label{fig:composition}
\end{figure}

@@

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/fig14.pdf}
\caption{GCM predictions (colored lines) compared to the best fit spherical harmonics model for the WFC3 white light, \Spitzer\ 3.6, and \Spitzer\ 4.5 micron phase curves (black lines, top to bottom). The nominal model is solar composition, cloud-free, with TiO/VO opacity and no drag. The models are corrected for the predicted ellipsoidal variability of the planet.}
\label{fig:gcmcomparison}
\end{figure}
